>

### 2020-09-24 manuscript/manuscript.Rmd
Address contributions more fully, close #9

In spite of its flexibility and basis in choice theory, utility-based
accessibility measures have not received much application in the accessibility
literature compared with distance-based or even gravity-based measures.
@Vale2016 present a descriptive classification of active accessibility techniques, and
explicitly dismiss utility-based metrics for incorporating randomness. The
accessibility formula presented in Equation \ref{eq:utility} is the expectation of a
random utility process, and is not in and of itself random any more than the
gravity model is random.
Utility-based accessibility metrics are commonly used, however, in alternatives
analyses of transit infrastructure improvements [@DeJong2007]. A reason for this
is likely that a regional travel demand model is available to the analysts, thus
making calibrated and multimodal logsums readily available [@Geurs2010].

>>>>

In spite of its flexibility and basis in choice theory, utility-based
accessibility measures have not received much application in the park accessibility
literature compared with distance-based or even gravity-based measures.
@Vale2016 present a descriptive classification of active accessibility techniques, and
explicitly dismiss utility-based metrics for incorporating randomness. This is 
a curious decision: The accessibility formula presented in Equation
\ref{eq:utility} is the expectation of a random utility process, but the measure
is not in and of itself random any more than the gravity model is random.
Utility-based accessibility metrics are commonly used, however, in alternatives
analyses of transit infrastructure improvements [@DeJong2007]. A reason for this
is likely that a regional travel demand model is available to the analysts, thus
making calibrated and multimodal logsums readily available [@Geurs2010].

To our knowledge, there has been no previous attempt to examine
access to parks in a metropolitan area using a utility-based definition as the
primary indicator of access. Consequently, there has also been no previous
effort to examine the effect of park access on health outcomes using this
theoretically attractive technique. In this study, we first develop a utility-based
measure of park access in New York City, and then apply this measure to study the
effect of access to public parks on aggregate health outcomes.
